Title Goes Here

### 2024-04-05 analysis/paper/paper.qmd

ggplot(jobdata_requirements_means) +
  aes(year_ad_posted, 
      mean_n,
      group = name) +
  geom_smooth(linewidth = 2,
              colour = "black") +
  geom_jitter(data = jobdata_requirements,
             aes(year_ad_posted, 
                 value),
             alpha = 0.1,
             height = 0.2,
             width =  0.1) +
  facet_wrap(~name,
             scales = "free_y") +
  xlab("Year") +
  ylab("Number requested in job ad") +
  scale_y_continuous(breaks = integer_breaks()) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

ggsave(here("analysis",
            "figures", 
            "fig-requirements-per-year.png"),
       bg ="white",
       h = 5, # experiment with h and w to get the right size and proportion 
       w = 8,
       units = "in",
       dpi = 600) # make the image nice and crisp

@@

ggplot() +
  geom_smooth(data =  jobdata_geo_year_tally,
            aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
            size = 2,
           se = FALSE #,
           # position=position_jitter(w=0.05, h=0.0)
           ) +
   geom_point(data = jobdata_geo_year_tally_max,
              aes(year_ad_posted,
                  prop,
                  group = name,
                  colour = name),
              size = 5) +
   geom_text_repel(data = jobdata_geo_year_tally_max,
             aes(year_ad_posted,
                 prop ,
                 group = name,
                 colour = name,
                 label = name),
             nudge_y = 0.01,
             bg.color = "white",
             bg.r = 0.25,
             size = 3) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()

ggsave(here("analysis",
            "figures", 
            "fig-geo-focus-by-year.png"),
       bg ="white")

@@

ggplot() +
  geom_smooth(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 2,
           # n = 10,
           span = 0.7,
           # position=position_jitter(w=0.05, h=0.0),
            se = FALSE) +
  # geom_point(data = jobdata_topic_year_tally_max,
  #            aes(year_ad_posted,
  #                prop,
  #                group = name,
  #                colour = name),
  #            size = 10) +
  # geom_text_repel(data = jobdata_topic_year_tally_max,
  #                 aes(year_ad_posted,
  #                     prop ,
  #                     group = name,
  #                     colour = name,
  #                     label = name),
  #                 nudge_y = 0.01,
  #                 bg.color = "white",
  #                 bg.r = 0.25,
  #                 size = 3) +
  # explore direct labels
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()

ggsave(here("analysis",
            "figures", 
            "fig-topic-focus-by-year.png"),
       bg ="white")

>>>>

ggplot(jobdata_requirements_means) +
  aes(year_ad_posted, 
      mean_n,
      group = name) +
  geom_smooth(linewidth = 2,
              colour = "black") +
  geom_jitter(data = jobdata_requirements,
             aes(year_ad_posted, 
                 value),
             alpha = 0.1,
             height = 0.2,
             width =  0.1) +
  facet_wrap(~name,
             scales = "free_y",
             nrow = 2) +
  xlab("Year") +
  ylab("Number requested in job ad") +
  scale_y_continuous(breaks = integer_breaks()) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

ggsave(here("analysis",
            "figures", 
            "fig-requirements-per-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion 
       w = 25,
       units = "in",
       dpi = 900) # make the image nice and crisp

@@

ggplot() +
  geom_smooth(data =  jobdata_geo_year_tally,
            aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
            size = 2,
           se = FALSE 
           ) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  guides(colour = guide_legend("Geographic\nfocus",
                               label.position = "bottom")) +
    theme_minimal( base_size = 14) +
  theme(legend.position="bottom")

ggsave(here("analysis",
            "figures", 
            "fig-geo-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion 
       w = 12,
       units = "in",
       dpi = 900) # make the image nice and crisp)

@@

ggplot() +
  geom_smooth(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 2,
           span = 0.7,
            se = FALSE) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  guides(colour = guide_legend("Topic\nfocus",
                               label.position = "bottom")) +
    theme_minimal( base_size = 14) +
  theme(legend.position="bottom")

ggsave(here("analysis",
            "figures", 
            "fig-topic-focus-by-year.png"),
       bg ="white",
       h = 10, # experiment with h and w to get the right size and proportion
       w = 12,
       units = "in",
       dpi = 900) # make the image nice and crisp))
